The Concurrent Calculi Formalisation Benchmark

### 2023-10-05 paper/paper.tex
Add another note and fix a whitespace error.

The introduction of the influential POPLMark challenge~\cite{POPLMark}
spearheaded a shift to including mechanised proofs accompanying
published papers. POPLMark's abstract starts with an important
question: ``How close are we to a world where every paper on program-
ming languages is accompanied by an electronic appendix with machine-
checked proofs?''. Much progress has been done in that respect,
notably the POPLMark Reloaded~\cite{POPLMarkReloaded} challenge aims
to identify and develop best practices and tool support for proofs
using logical relations.

@@

\section{Design of the benchmark}
\subsection{Topics we discussed during the meetings}
- Linearity type system dual vs. Vasco's?
- Only linear channels or also unrestricted channels?
- Pi-calculus or CCS for linearity?
- Choice in general
  - Choice can be encoded, so is not necessary
  - Complicates the theory
  - Add as ``future work''
- Choice in scope extrusion
- Extension categories: other topics and small technical differences
- Why not unified syntax?
  - Choice and coinduction does not mix
- Different notions of bisimulation in the coinduction challenge
- Linearity: the context is polymorphic
- Coinduction: why is congruence interesting?
- Why are the challenges not covered by POPLMark/POPLMark Reloaded?
- Scope extrusion does not behave as ``normal'' a binder wrt. semantics, so the usual techniques may not work
- A goal is to build a culture of formalising things in the community
- Linearity is generally interesting
- Encoding techniques are not different from any other field, so there's nothing ``special'' about the formalisations here
- We don't care about the content of messages in coinduction, only synchronization
- Why explicitly bind two endpoints in linearity? To make the duality/polarity connection obvious
- Linearity: Do we care about avoiding deadlocks? No, this is stronger than safety as in well-formedness
- Asynchrony? Not necessary, this is a it more advanced
- ``Proper'' barbs with a structural congruence in coinduction instead of LTS semantics

>>>>

The introduction of the influential POPLMark challenge~\cite{POPLMark}
spearheaded a shift to including mechanised proofs accompanying
published papers. POPLMark's abstract starts with an important
question: ``How close are we to a world where every paper on programming languages is accompanied by an electronic appendix with machine-
checked proofs?''. Much progress has been done in that respect,
notably the POPLMark Reloaded~\cite{POPLMarkReloaded} challenge aims
to identify and develop best practices and tool support for proofs
using logical relations.

@@

\section{Design of the benchmark}
\subsection{Topics we discussed during the meetings}
- Linearity type system dual vs. Vasco's?
- Only linear channels or also unrestricted channels?
- Pi-calculus or CCS for linearity?
- Choice in general
  - Choice can be encoded, so is not necessary
  - Complicates the theory
  - Add as ``future work''
- Choice in scope extrusion
- Extension categories: other topics and small technical differences
- Why not unified syntax?
  - Choice and coinduction does not mix
- Different notions of bisimulation in the coinduction challenge
- Linearity: the context is polymorphic
- Coinduction: why is congruence interesting?
- Why are the challenges not covered by POPLMark/POPLMark Reloaded?
- Scope extrusion does not behave as ``normal'' a binder wrt. semantics, so the usual techniques may not work
- A goal is to build a culture of formalising things in the community
- Linearity is generally interesting
- Encoding techniques are not different from any other field, so there's nothing ``special'' about the formalisations here
- We don't care about the content of messages in coinduction, only synchronization
- Why explicitly bind two endpoints in linearity? To make the duality/polarity connection obvious
- Linearity: Do we care about avoiding deadlocks? No, this is stronger than safety as in well-formedness
- Asynchrony? Not necessary, this is a it more advanced
- Why do we keep the restrictions around in the LTS semantics in scope extrusion?
- ``Proper'' barbs with a structural congruence in coinduction instead of LTS semantics
